---
title: "TidyTemplate"
date: 2022-08-01
output: html_document
---

# TidyTuesday

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidytuesdayR, tidyverse)
library(lubridate)
library(hrbrthemes)
library(MetBrewer)


```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r}
tt
```

```{r Load}

tt <- tt_load("2022-08-02")

```

# Readme

Take a look at the readme for the weekly data to get insight on the dataset. This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

f <- tt$frogs
f |> head()

```

# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}



```

# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}

f |> 
  count(Water, sort=TRUE) |> 
  mutate(Water = fct_reorder(Water, n)) |> 
  ggplot(aes(Water, n, fill = Water)) + 
  geom_col(show.legend = F)+
  theme_ft_rc()
  

  
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter!

```{r}

# This will save your most recent plot
ggsave(
  filename = "My TidyTuesday Plot.png",
  device = "png")

```
